Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-11 hscc2017/paper.tex
hscc17

The digital controllers synthesized using the algorithm we present in this
paper are typically used in closed loops with continuous (physical) plants. 
Thus, we consider continuous dynamics (the plant) and discrete parts (the
digital controller).  To obtain a joint model, we fully discretize the
continuous plant.  We briefly recall the standard foundations of this step.

We only consider transfer function models, and require a $z$-domain transfer
function $G(z)$ that captures all aspects of the continuous plant with a
Laplace domain transfer function $G(s)$ and the sampling and hold process. 
The continuous model of the plant must be discretized to obtain the
corresponding coefficients of $G(z)$.

@@

Among the discretization methods in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is suitable for representing the sample
and hold processes in complex systems~\cite{istepanian2012digital}.  The ZOH
discretization models the exact effect of sampling and DAC interpolation
over the plant.

>>>>

The digital controllers synthesized using the algorithm we present in this
paper are typically used in closed loops with continuous (physical) plants. 
Thus, we consider continuous dynamics (the plant) and discrete parts (the
digital controller). In order to obtain an overall model, we discretize the
continuous plant and look at the plant dynamics from the perspective of the digital controller. 
%We briefly recall the standard foundations of this step.

As we only consider transfer function models, and require a $z$-domain transfer
function $G(z)$ that captures all aspects of the continuous plant, 
which is naturally described via a Laplace-domain transfer function $G(s)$. 
% and the sampling and hold process. 
The continuous model of the plant must be discretized to obtain the
corresponding coefficients of $G(z)$.

@@

Among the discretization methods in the literature~\cite{Franklin15}, 
%the zero-order hold (ZOH) discretization is suitable for representing 
we consider the sample-and-hold processes in complex systems~\cite{istepanian2012digital}.  
On the other hand, 
the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
